Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach

### 2013-08-26 inst/doc/nonparametric-bayes.tex
updated run from zero

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage{color}
\usepackage{fancyvrb}
\DefineShortVerb[commandchars=\\\{\}]{\|}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\newenvironment{Shaded}{}{}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
\newcommand{\RegionMarkerTok}[1]{{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\NormalTok}[1]{{#1}}
\usepackage{graphicx}
% We will generate all images so they have a width \maxwidth. This means
% that they will get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}
% Pandoc header

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{options}\NormalTok{(}\DataTypeTok{xtable.print.comment =} \OtherTok{FALSE}\NormalTok{)}
\KeywordTok{options}\NormalTok{(}\DataTypeTok{xtable.type =} \StringTok{"latex"}\NormalTok{, }\DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{)}
\NormalTok{opts_knit$}\KeywordTok{set}\NormalTok{(}\DataTypeTok{progress =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{verbose =} \OtherTok{TRUE}\NormalTok{)}
\NormalTok{opts_chunk$}\KeywordTok{set}\NormalTok{(}\DataTypeTok{dev =} \KeywordTok{c}\NormalTok{(}\StringTok{"pdf"}\NormalTok{, }\StringTok{"png"}\NormalTok{), }\DataTypeTok{fig.width =} \FloatTok{5.5}\NormalTok{, }\DataTypeTok{fig.height =} \DecValTok{4}\NormalTok{, }\DataTypeTok{cache.path =} \StringTok{"cache/nonparametric-bayes/"}\NormalTok{, }
    \DataTypeTok{cache =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{external =} \OtherTok{TRUE}\NormalTok{)}
\NormalTok{opts_chunk$}\KeywordTok{set}\NormalTok{(}\DataTypeTok{warning =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{message =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{comment =} \OtherTok{NA}\NormalTok{, }\DataTypeTok{tidy =} \OtherTok{FALSE}\NormalTok{)}
\NormalTok{toggle = }\StringTok{"markup"}
\KeywordTok{theme_set}\NormalTok{(}\KeywordTok{theme_bw}\NormalTok{(}\DataTypeTok{base_size =} \DecValTok{12}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{require}\NormalTok{(modeest)}
\NormalTok{posterior.mode <- function(x) \{}
  \KeywordTok{mlv}\NormalTok{(x, }\DataTypeTok{method=}\StringTok{"shorth"}\NormalTok{)$M}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{f <- RickerAllee}
\NormalTok{p <- }\KeywordTok{c}\NormalTok{(}\DecValTok{2}\NormalTok{, }\DecValTok{8}\NormalTok{, }\DecValTok{5}\NormalTok{)}
\NormalTok{K <- }\DecValTok{10}  \CommentTok{# approx, a li'l' less}
\NormalTok{allee <- }\DecValTok{5} \CommentTok{# approx, a li'l' less}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{sigma_g <- }\FloatTok{0.05}
\NormalTok{sigma_m <- }\FloatTok{0.0}
\NormalTok{z_g <- function() }\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{, sigma_g)}
\NormalTok{z_m <- function() }\DecValTok{1}
\NormalTok{x_grid <- }\KeywordTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{1.5} \NormalTok{* K, }\DataTypeTok{length=}\DecValTok{50}\NormalTok{)}
\NormalTok{h_grid <- x_grid}
\NormalTok{profit <- function(x,h) }\KeywordTok{pmin}\NormalTok{(x, h)}
\NormalTok{delta <- }\FloatTok{0.01}
\NormalTok{OptTime <- }\DecValTok{50}  \CommentTok{# stationarity with unstable models is tricky thing}
\NormalTok{reward <- }\DecValTok{0}
\NormalTok{xT <- }\DecValTok{0}
\NormalTok{Xo <-  allee}\FloatTok{+.5}\CommentTok{# observations start from}
\NormalTok{x0 <- K }\CommentTok{# simulation under policy starts from}
\NormalTok{Tobs <- }\DecValTok{40}
\NormalTok{MaxT = }\DecValTok{1000} \CommentTok{# timeout for value iteration convergence}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
  \KeywordTok{set.seed}\NormalTok{(}\DecValTok{1234}\NormalTok{)}
  \CommentTok{#harvest <- sort(rep(seq(0, .5, length=7), 5))}
  \NormalTok{x <- }\KeywordTok{numeric}\NormalTok{(Tobs)}
  \NormalTok{x[}\DecValTok{1}\NormalTok{] <- Xo}
  \NormalTok{nz <- }\DecValTok{1}
  \NormalTok{for(t in }\DecValTok{1}\NormalTok{:(Tobs}\DecValTok{-1}\NormalTok{))}
    \NormalTok{x[t}\DecValTok{+1}\NormalTok{] = }\KeywordTok{z_g}\NormalTok{() * }\KeywordTok{f}\NormalTok{(x[t], }\DataTypeTok{h=}\DecValTok{0}\NormalTok{, }\DataTypeTok{p=}\NormalTok{p)}
  \NormalTok{obs <- }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{x =} \KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nz), }
                          \KeywordTok{pmax}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,Tobs}\DecValTok{-1}\NormalTok{), x[}\DecValTok{1}\NormalTok{:(Tobs}\DecValTok{-1}\NormalTok{)])), }
                    \DataTypeTok{y =} \KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nz), }
                          \NormalTok{x[}\DecValTok{2}\NormalTok{:Tobs]))}
\NormalTok{raw_plot <- }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{time =} \DecValTok{1}\NormalTok{:Tobs, }\DataTypeTok{x=}\NormalTok{x), }\KeywordTok{aes}\NormalTok{(time,x)) + }\KeywordTok{geom_line}\NormalTok{()}
\NormalTok{raw_plot}
\end{Highlighting}
\end{Shaded}

\begin{figure}[htbp]
\centering
\includegraphics{figure/obs.pdf}
\caption{plot of chunk obs}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{12345}\NormalTok{)}
\NormalTok{estf <- function(p)\{ }
    \NormalTok{mu <- }\KeywordTok{f}\NormalTok{(obs$x,}\DecValTok{0}\NormalTok{,p)}
    \NormalTok{-}\KeywordTok{sum}\NormalTok{(}\KeywordTok{dlnorm}\NormalTok{(obs$y, }\KeywordTok{log}\NormalTok{(mu), p[}\DecValTok{4}\NormalTok{]), }\DataTypeTok{log=}\OtherTok{TRUE}\NormalTok{)}
\NormalTok{\}}
\NormalTok{par <- }\KeywordTok{c}\NormalTok{(p[}\DecValTok{1}\NormalTok{]*}\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{,.}\DecValTok{1}\NormalTok{), }
         \NormalTok{p[}\DecValTok{2}\NormalTok{]*}\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{,.}\DecValTok{1}\NormalTok{), }
         \NormalTok{p[}\DecValTok{3}\NormalTok{]*}\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{, .}\DecValTok{1}\NormalTok{), }
         \NormalTok{sigma_g * }\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{,.}\DecValTok{1}\NormalTok{))}
\NormalTok{o <- }\KeywordTok{optim}\NormalTok{(par, estf, }\DataTypeTok{method=}\StringTok{"L"}\NormalTok{, }\DataTypeTok{lower=}\KeywordTok{c}\NormalTok{(}\FloatTok{1e-5}\NormalTok{,}\FloatTok{1e-5}\NormalTok{,}\FloatTok{1e-5}\NormalTok{,}\FloatTok{1e-5}\NormalTok{))}
\NormalTok{f_alt <- f}
\NormalTok{p_alt <- }\KeywordTok{c}\NormalTok{(}\KeywordTok{as.numeric}\NormalTok{(o$par[}\DecValTok{1}\NormalTok{]), }\KeywordTok{as.numeric}\NormalTok{(o$par[}\DecValTok{2}\NormalTok{]), }\KeywordTok{as.numeric}\NormalTok{(o$par[}\DecValTok{3}\NormalTok{]))}
\NormalTok{sigma_g_alt <- }\KeywordTok{as.numeric}\NormalTok{(o$par[}\DecValTok{4}\NormalTok{])}

\NormalTok{est <- }\KeywordTok{list}\NormalTok{(}\DataTypeTok{f =} \NormalTok{f_alt, }\DataTypeTok{p =} \NormalTok{p_alt, }\DataTypeTok{sigma_g =} \NormalTok{sigma_g_alt, }\DataTypeTok{mloglik=}\NormalTok{o$value)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{true_means <- }\KeywordTok{sapply}\NormalTok{(x_grid, f, }\DecValTok{0}\NormalTok{, p)}
\NormalTok{est_means <- }\KeywordTok{sapply}\NormalTok{(x_grid, est$f, }\DecValTok{0}\NormalTok{, est$p)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#inv gamma has mean b / (a - 1) (assuming a>1) and variance b ^ 2 / ((a - 2) * (a - 1) ^ 2) (assuming a>2)}
\NormalTok{s2.p <- }\KeywordTok{c}\NormalTok{(}\DecValTok{5}\NormalTok{,}\DecValTok{5}\NormalTok{)  }
\NormalTok{d.p = }\KeywordTok{c}\NormalTok{(}\DecValTok{10}\NormalTok{, }\DecValTok{1}\NormalTok{/}\FloatTok{0.1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{gp <- }\KeywordTok{gp_mcmc}\NormalTok{(obs$x, }\DataTypeTok{y=}\NormalTok{obs$y, }\DataTypeTok{n=}\FloatTok{1e5}\NormalTok{, }\DataTypeTok{s2.p =} \NormalTok{s2.p, }\DataTypeTok{d.p =} \NormalTok{d.p)}
\NormalTok{gp_dat <- }\KeywordTok{gp_predict}\NormalTok{(gp, x_grid, }\DataTypeTok{burnin=}\FloatTok{1e4}\NormalTok{, }\DataTypeTok{thin=}\DecValTok{300}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{gp_assessment_plots <- }\KeywordTok{summary_gp_mcmc}\NormalTok{(gp, }\DataTypeTok{burnin=}\FloatTok{1e4}\NormalTok{, }\DataTypeTok{thin=}\DecValTok{300}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Summarize the GP model}
\NormalTok{tgp_dat <- }
    \KeywordTok{data.frame}\NormalTok{(  }\DataTypeTok{x =} \NormalTok{x_grid, }
                 \DataTypeTok{y =} \NormalTok{gp_dat$E_Ef, }
                 \DataTypeTok{ymin =} \NormalTok{gp_dat$E_Ef - }\DecValTok{2} \NormalTok{* }\KeywordTok{sqrt}\NormalTok{(gp_dat$E_Vf), }
                 \DataTypeTok{ymax =} \NormalTok{gp_dat$E_Ef + }\DecValTok{2} \NormalTok{* }\KeywordTok{sqrt}\NormalTok{(gp_dat$E_Vf) )}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{y <- x }
\NormalTok{N <- }\KeywordTok{length}\NormalTok{(x);}
\NormalTok{jags.data <- }\KeywordTok{list}\NormalTok{(}\StringTok{"N"}\NormalTok{,}\StringTok{"y"}\NormalTok{)}
\NormalTok{n.chains <- }\DecValTok{6}
\NormalTok{n.iter <- }\FloatTok{1e6}
\NormalTok{n.burnin <- }\KeywordTok{floor}\NormalTok{(}\DecValTok{10000}\NormalTok{)}
\NormalTok{n.thin <- }\KeywordTok{max}\NormalTok{(}\DecValTok{1}\NormalTok{, }\KeywordTok{floor}\NormalTok{(n.chains * (n.iter - n.burnin)/}\DecValTok{1000}\NormalTok{))}
\NormalTok{n.update <- }\DecValTok{10}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{stdQ_prior_p <- }\KeywordTok{c}\NormalTok{(}\FloatTok{1e-6}\NormalTok{, }\DecValTok{100}\NormalTok{)}
\NormalTok{stdR_prior_p <- }\KeywordTok{c}\NormalTok{(}\FloatTok{1e-6}\NormalTok{, .}\DecValTok{1}\NormalTok{)}
\NormalTok{stdQ_prior  <- function(x) }\KeywordTok{dunif}\NormalTok{(x, stdQ_prior_p[}\DecValTok{1}\NormalTok{], stdQ_prior_p[}\DecValTok{2}\NormalTok{])}
\NormalTok{stdR_prior  <- function(x) }\KeywordTok{dunif}\NormalTok{(x, stdR_prior_p[}\DecValTok{1}\NormalTok{], stdR_prior_p[}\DecValTok{2}\NormalTok{])}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{K_prior_p <- }\KeywordTok{c}\NormalTok{(}\FloatTok{0.01}\NormalTok{, }\FloatTok{20.0}\NormalTok{)}
\NormalTok{r0_prior_p <- }\KeywordTok{c}\NormalTok{(}\FloatTok{0.01}\NormalTok{, }\FloatTok{6.0}\NormalTok{)}
\NormalTok{theta_prior_p <- }\KeywordTok{c}\NormalTok{(}\FloatTok{0.01}\NormalTok{, }\FloatTok{20.0}\NormalTok{)}

\NormalTok{bugs.model <- }
\KeywordTok{paste}\NormalTok{(}\KeywordTok{sprintf}\NormalTok{(}
\StringTok{"model\{}
\StringTok{  K     ~ dunif(%s, %s)}
\StringTok{  r0    ~ dunif(%s, %s)}
\StringTok{  theta ~ dunif(%s, %s)}
\StringTok{  stdQ ~ dunif(%s, %s)"}\NormalTok{, }
  \NormalTok{K_prior_p[}\DecValTok{1}\NormalTok{], K_prior_p[}\DecValTok{2}\NormalTok{],}
  \NormalTok{r0_prior_p[}\DecValTok{1}\NormalTok{], r0_prior_p[}\DecValTok{2}\NormalTok{],}
  \NormalTok{theta_prior_p[}\DecValTok{1}\NormalTok{], theta_prior_p[}\DecValTok{2}\NormalTok{],}
  \NormalTok{stdQ_prior_p[}\DecValTok{1}\NormalTok{], stdQ_prior_p[}\DecValTok{2}\NormalTok{]),}

  \StringTok{"}
\StringTok{  iQ <- 1 / (stdQ * stdQ);}
\StringTok{  y[1] ~ dunif(0, 10)}
\StringTok{  for(t in 1:(N-1))\{}
\StringTok{    mu[t] <- log(y[t]) + r0 * (1 - y[t]/K)* (y[t] - theta) / K }
\StringTok{    y[t+1] ~ dlnorm(mu[t], iQ) }
\StringTok{  \}}
\StringTok{\}"}\NormalTok{)}
\KeywordTok{writeLines}\NormalTok{(bugs.model, }\StringTok{"allen_process.bugs"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{K_prior     <- function(x) }\KeywordTok{dunif}\NormalTok{(x, K_prior_p[}\DecValTok{1}\NormalTok{], K_prior_p[}\DecValTok{2}\NormalTok{])}
\NormalTok{r0_prior <- function(x) }\KeywordTok{dunif}\NormalTok{(x, r0_prior_p[}\DecValTok{1}\NormalTok{], r0_prior_p[}\DecValTok{2}\NormalTok{])}
\NormalTok{theta_prior <- function(x) }\KeywordTok{dunif}\NormalTok{(x, theta_prior_p[}\DecValTok{1}\NormalTok{], theta_prior_p[}\DecValTok{2}\NormalTok{])}
\NormalTok{par_priors  <- }\KeywordTok{list}\NormalTok{(}\DataTypeTok{K =} \NormalTok{K_prior, }\DataTypeTok{deviance =} \NormalTok{function(x) }\DecValTok{0} \NormalTok{* x, }
                    \DataTypeTok{r0 =} \NormalTok{r0_prior, }\DataTypeTok{theta =} \NormalTok{theta_prior,}
                    \DataTypeTok{stdQ =} \NormalTok{stdQ_prior)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{jags.params=}\KeywordTok{c}\NormalTok{(}\StringTok{"K"}\NormalTok{,}\StringTok{"r0"}\NormalTok{,}\StringTok{"theta"}\NormalTok{,}\StringTok{"stdQ"}\NormalTok{) }\CommentTok{# be sensible about the order here}
\NormalTok{jags.inits <- function()\{}
  \KeywordTok{list}\NormalTok{(}\StringTok{"K"}\NormalTok{= }\DecValTok{10} \NormalTok{* }\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{, }\FloatTok{0.1}\NormalTok{),}
       \StringTok{"r0"}\NormalTok{= }\DecValTok{1} \NormalTok{* }\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{, }\FloatTok{0.1}\NormalTok{) ,}
       \StringTok{"theta"}\NormalTok{=   }\DecValTok{5} \NormalTok{* }\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{, }\FloatTok{0.1}\NormalTok{) , }
       \StringTok{"stdQ"}\NormalTok{= }\KeywordTok{abs}\NormalTok{( }\FloatTok{0.1} \NormalTok{* }\KeywordTok{rlnorm}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{0}\NormalTok{, }\FloatTok{0.1}\NormalTok{)),}
       \DataTypeTok{.RNG.name=}\StringTok{"base::Wichmann-Hill"}\NormalTok{, }\DataTypeTok{.RNG.seed=}\DecValTok{123}\NormalTok{)}
\NormalTok{\}}

\KeywordTok{set.seed}\NormalTok{(}\DecValTok{1234}\NormalTok{)}
\CommentTok{# parallel refuses to take variables as arguments (e.g. n.iter = 1e5 works, but n.iter = n doesn't)}
\NormalTok{allen_jags <- }\KeywordTok{do.call}\NormalTok{(jags.parallel, }\KeywordTok{list}\NormalTok{(}\DataTypeTok{data=}\NormalTok{jags.data, }\DataTypeTok{inits=}\NormalTok{jags.inits, }
                                      \NormalTok{jags.params, }\DataTypeTok{n.chains=}\NormalTok{n.chains, }
                                      \DataTypeTok{n.iter=}\NormalTok{n.iter, }\DataTypeTok{n.thin=}\NormalTok{n.thin, }
                                      \DataTypeTok{n.burnin=}\NormalTok{n.burnin, }
                                      \DataTypeTok{model.file=}\StringTok{"allen_process.bugs"}\NormalTok{))}

\CommentTok{# Run again iteratively if we haven't met the Gelman-Rubin convergence criterion}
\KeywordTok{recompile}\NormalTok{(allen_jags) }\CommentTok{# required for parallel}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 328

Initializing model

Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 328

Initializing model

Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 328

Initializing model

Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 328

Initializing model

Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 328

Initializing model

Compiling model graph
   Resolving undeclared variables
   Allocating nodes
   Graph Size: 328

Initializing model
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{allen_jags <- }\KeywordTok{do.call}\NormalTok{(autojags, }
                                            \KeywordTok{list}\NormalTok{(}\DataTypeTok{object=}\NormalTok{allen_jags, }\DataTypeTok{n.update=}\NormalTok{n.update, }
                           \DataTypeTok{n.iter=}\NormalTok{n.iter, }\DataTypeTok{n.thin =} \NormalTok{n.thin))}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{tmp <- }\KeywordTok{lapply}\NormalTok{(}\KeywordTok{as.mcmc}\NormalTok{(allen_jags), as.matrix) }\CommentTok{# strip classes the hard way...}
\NormalTok{allen_posteriors <- }\KeywordTok{melt}\NormalTok{(tmp, }\DataTypeTok{id =} \KeywordTok{colnames}\NormalTok{(tmp[[}\DecValTok{1}\NormalTok{]])) }
\KeywordTok{names}\NormalTok{(allen_posteriors) = }\KeywordTok{c}\NormalTok{(}\StringTok{"index"}\NormalTok{, }\StringTok{"variable"}\NormalTok{, }\StringTok{"value"}\NormalTok{, }\StringTok{"chain"}\NormalTok{)}
\NormalTok{plot_allen_traces <- }\KeywordTok{ggplot}\NormalTok{(allen_posteriors) + }\KeywordTok{geom_line}\NormalTok{(}\KeywordTok{aes}\NormalTok{(index, value)) + }
  \KeywordTok{facet_wrap}\NormalTok{(~ variable, }\DataTypeTok{scale=}\StringTok{"free"}\NormalTok{, }\DataTypeTok{ncol=}\DecValTok{1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{allen_priors <- }\KeywordTok{ddply}\NormalTok{(allen_posteriors, }\StringTok{"variable"}\NormalTok{, function(dd)\{}
    \NormalTok{grid <- }\KeywordTok{seq}\NormalTok{(}\KeywordTok{min}\NormalTok{(dd$value), }\KeywordTok{max}\NormalTok{(dd$value), }\DataTypeTok{length =} \DecValTok{100}\NormalTok{) }
    \KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{value =} \NormalTok{grid, }\DataTypeTok{density =} \NormalTok{par_priors[[dd$variable[}\DecValTok{1}\NormalTok{]]](grid))}
\NormalTok{\})}
\NormalTok{plot_allen_posteriors <- }\KeywordTok{ggplot}\NormalTok{(allen_posteriors, }\KeywordTok{aes}\NormalTok{(value)) + }
  \KeywordTok{stat_density}\NormalTok{(}\DataTypeTok{geom=}\StringTok{"path"}\NormalTok{, }\DataTypeTok{position=}\StringTok{"identity"}\NormalTok{, }\DataTypeTok{alpha=}\FloatTok{0.7}\NormalTok{) +}
  \KeywordTok{geom_line}\NormalTok{(}\DataTypeTok{data=}\NormalTok{allen_priors, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{value, }\DataTypeTok{y=}\NormalTok{density), }\DataTypeTok{col=}\StringTok{"red"}\NormalTok{) + }
  \KeywordTok{facet_wrap}\NormalTok{(~ variable, }\DataTypeTok{scale=}\StringTok{"free"}\NormalTok{, }\DataTypeTok{ncol=}\DecValTok{3}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{A <- allen_posteriors}
\NormalTok{A$index <- A$index + A$chain * }\KeywordTok{max}\NormalTok{(A$index) }\CommentTok{# Combine samples across chains by renumbering index }
\NormalTok{pardist <- }\KeywordTok{acast}\NormalTok{(A, index ~ variable)}
\NormalTok{bayes_coef <- }\KeywordTok{apply}\NormalTok{(pardist,}\DecValTok{2}\NormalTok{, posterior.mode) }
\NormalTok{bayes_pars <- }\KeywordTok{unname}\NormalTok{(}\KeywordTok{c}\NormalTok{(bayes_coef[}\StringTok{"r0"}\NormalTok{], bayes_coef[}\StringTok{"K"}\NormalTok{], bayes_coef[}\StringTok{"theta"}\NormalTok{])) }\CommentTok{# parameters formatted for f}
\NormalTok{allen_f <- function(x,h,p) }\KeywordTok{unname}\NormalTok{(}\KeywordTok{RickerAllee}\NormalTok{(x,h, }\KeywordTok{unname}\NormalTok{(p[}\KeywordTok{c}\NormalTok{(}\StringTok{"r0"}\NormalTok{, }\StringTok{"K"}\NormalTok{, }\StringTok{"theta"}\NormalTok{)])))}
\NormalTok{allen_means <- }\KeywordTok{sapply}\NormalTok{(x_grid, f, }\DecValTok{0}\NormalTok{, bayes_pars)}
\NormalTok{bayes_pars}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
[1] 0.5003 7.7115 4.6039
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{head}\NormalTok{(pardist)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
        K deviance     r0    stdQ theta
170 7.898    34.41 0.6668 0.05566 3.956
171 7.745    32.76 0.7554 0.05137 4.668
172 7.577    31.66 1.0705 0.04562 4.073
173 7.859    31.26 1.5647 0.04238 5.087
174 7.821    30.67 1.7348 0.04662 5.230
175 8.003    34.90 1.4495 0.05005 5.444
\end{verbatim}

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage{color}
\usepackage{fancyvrb}
\DefineShortVerb[commandchars=\\\{\}]{\|}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\newenvironment{Shaded}{}{}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
\newcommand{\RegionMarkerTok}[1]{{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\NormalTok}[1]{{#1}}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}
% Pandoc header

@@
